---
title: "Math 253 Final Project- H-1B Visa Analysis"
author: "Melissa Leong & Muath Ibaid"
date: "4/18/2017"
output: html_document
---

## **a) Problem Setting**: 
**The Client:** An H1B visa applicant
**The Situation:** The client walks in and requests that we to predict their chances of being approved for and H1B visa. The client is able to provide information on their: intended work sector, prevailing wage, whether their position is full time or part time amd the year they applied. 

------------------------------------

## **b) Data Description**: 

```{r, include=FALSE}
#Load libraries
install.packages("data.table")
library(mosaic)
library(readr)
library(data.table)
library(MASS)
   
#load data
h1b <- read.csv("/home/local/MAC/mleong/Math-253-Assignments/h1b_kaggle.csv")
h1bSmall <- h1b[PREVAILING_WAGE=3607]

#Type transformations
h1b$outcome <- as.numeric(with(h1b,CASE_STATUS=="CERTIFIED"))
h1b$PREVAILING_WAGE <- as.integer(h1b$PREVAILING_WAGE)

```


#### Declaring Test and training data
```{r}
tr = (h1b$X %% 2 == 0)
te = (!tr)

training = h1b[tr, ]
testing = h1b[te, ]


training$outcome <- as.factor(training$outcome)
testing$outcome <- as.factor(testing$outcome)

```



------------------------------------

## **c) Classification and regression methods**:  

### c.1 Logistic Regression:
MEL DOES THIS 
```{r}
#training: 

mc1 = glm(outcome ~  PREVAILING_WAGE, data = training)
#mc1 = glm(outcome ~  , data = training)

#summary(h1b$X)
```


### c.2 Linear Disciminate Analysis (LDA) / Quadratic Discriminate Analysis (QDA):
MUATH DOES THIS

```{r}
mlda = lda(outcome ~ PREVAILING_WAGE + FULL_TIME_POSITION, data = training)
plot(mlda)
```



------------------------------------
## **d) Evaluation of results:** 

*** Loss funciton: correct and incorrect classifications -- 



------------------------------------
## **d) Recommendations:** 

